---
Title: "installing and seting up R"
Author: "Martin chege"
Date: "7/13/2020"
Output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is article will take you through  installing R and Rstudio together with  the basic packages that will be required to keep you going with your projects use this link to get more info<http://.rstudio.com>.



```{r }

```




##<u>installing R</u>




## Step1 Downloading the r setup

Download link <https://ww.r-project.org>

```{r }
# to download the r setup follow the link provided in the above link to download the latest r

#click the download CRAN button
```

## Step 2 Choose the mirror you would want to download
```{r}
#selecting the mirror

```


## Step 3 Further based on operating system that you use select the lelevat link
```{r}
# sectionof the correct operating system that you are using
```

## step 4 Select <b>R from first time</b>
```{r}
#clicking on the r link
```

## Step 5 Download and run the executable file
```{r}
#download the windows version  if using windows
#then click the .exe that was downloaded to install it in the default library
```




## <u>Installing R Studio</u>





```{r}
#lets now install the main GUI that we are going to be using as out text editor
```

## Step 1 Donwload Rstudio From 
DOWNLOAD LINK<https://www.rstudio.com/products/rstudio/download/>
```{r}
#use the link above
```

## Step 2 Based on OS choose the relevant executable installer and download it
```{r}
#choode the .exe for windows
```

## Step 3 Run the downloaded installer and start installing it in the default location
``.exe ``

```{R}
#run the .exe so that you install rstudio
```




## <u>Packages Installation </u>


## Step 1 click inside the console 
general case ``install.packages("pakagename")``
eg ``install.packages("raster")``

```{r}
#type inside the console uncomenting install.packages


#install.packages("pakagename")
#eg

#install.packages("raster")

#then hit enter anw wait for it to download
```







